A Hitchhiker's Guide to Reproducible Research

### 2021-06-09 manuscript.Rmd

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output: bookdown::pdf_document2
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
abstract: "`r tryCatch(trimws(readr::read_file('abstract.Rmd')))`"
---

<!-- the HTML comments, like this one, are meta comments, mainly describing the intent --->
<!-- each sentence below a heading summarizes what I want to say there --->
<!-- "Hands-on:" means concrete practical application, they roughly proceed from easy/familiar to hard/unfamiliar-->

@@

[^popper]: In fact, @popperLogicScientificDiscovery2002's famous criterion of demarcation is built around "inter-subjective testing", a concept which he later generalised to inter-subjective criticism (Footnote *¹, p. 22). Somewhat confusingly, @popperLogicScientificDiscovery2002 uses the term "Reproducibility" for what we would call "Replication".

@@

First, to resolve ambiguity across multiple versions of code and data that come into existence during the development phase of a research project, we recommend using a **version control** system.
Version control allows a clear link between which results were generated by which version of code and data.

A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
A version-controlled project makes the loss of files unlikely and also supports remote collaboration.

@@

\@ref{schematic}

To summarize, the workflow by @Peikert2019 requires four components (see Figure \@ref{schematic}), dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), containerization (using Docker).
While R Markdown and git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside studies of information technology, which represents a considerable hurdle in the acceptance and implementation of the workflow.
To remove this hurdle, we have developed a new R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R.
In the remainder, we will walk you through a complete research project, from sketching the very first idea over preregistration, data analysis, and submission of a preprint while focusing on how the `repro`-package enables users to maintain reproducibility of all steps.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency tracking (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

```{r, include=FALSE}
knitr::write_bib(
  c(
    .packages(),
    "repro",
    "here",
    "rticles",
    "gert",
    "bookdown",
    "lavaan",
    "knitr",
    "targets",
    "renv",
    "tidyverse"
  ),
  "packages.bib"
)
```

>>>>

---
title: A Hitchhiker's Guide to Reproducible Research
author:
  - name: Aaron Peikert
    affil: 1, *
    orcid: 0000-0001-7813-818X
  - name: Caspar J. Van Lissa
    affil: 2, 3
    orcid: 0000-0002-0808-5024
  - name: Andreas M. Brandmaier
    affil: 1, 4
    orcid: 0000-0001-8765-6982
affiliation:
  - num: 1
    address: |
      Center for Lifespan Psychology---Max Planck Institute for Human Development
      Lentzeallee 94, 14195 Berlin, Germany
  - num: 2
    address: |
      Department of Methodology & Statistics---Utrecht University faculty of Social and Behavioral Sciences, Utrecht, Netherlands
  - num: 3
    address: |
      Open Science Community Utrecht, Utrecht, Netherlands
  - num: 4
    address: |
      Max Planck UCL Centre for Computational Psychiatry and Ageing Research
      Berlin, Germany and London, UK
# firstnote to eighthnote
correspondence: |
  peikert@mpib-berlin.mpg.de
journal: psych
type: tutorial
status: submit
bibliography: temp.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: "`r tryCatch(trimws(readr::read_file(here::here('abstract.Rmd'))))`"
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  The authors declare no conflict of interest.
abbreviations:
  - short: GUI
    long: Graphical User Interface
  - short: CLI
    long: Comand Line Interface
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
output:
  bookdown::markdown_document2:
    base_format: rticles::mdpi_article
header-includes:
   - \usepackage[labelformat=empty]{caption}
---

@@

[^popper]: In fact, @popperLogicScientificDiscovery2002's famous criterion of demarcation is built around "inter-subjective testing", a concept which he later generalised to inter-subjective criticism (Footnote *1, p. 22). Somewhat confusingly, @popperLogicScientificDiscovery2002 uses the term "Reproducibility" for what we would call "Replication".

@@

First, to resolve ambiguity across multiple versions of code and data that come into existence during the development phase of a research project, we recommend using a **version control** system.
Version control allows a clear link between which results were generated by which version of code and data.
A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
A version-controlled project makes the loss of files unlikely and also supports remote collaboration.

@@

To summarize, the workflow by @Peikert2019 requires four components (see Figure \@ref(fig:schematic)), dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), containerization (using Docker).
While R Markdown and git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside studies of information technology, which represents a considerable hurdle in the acceptance and implementation of the workflow.
To remove this hurdle, we have developed a new R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R.
In the remainder, we will walk you through a complete research project, from sketching the very first idea over preregistration, data analysis, and submission of a preprint while focusing on how the `repro`-package enables users to maintain reproducibility of all steps.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency tracking (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics(here::here("images/nutshell.svg"), auto_pdf = TRUE)
```

@@

```{r, include=FALSE}
knitr::write_bib(
  c(
    .packages(),
    "repro",
    "here",
    "rticles",
    "gert",
    "bookdown",
    "lavaan",
    "knitr",
    "targets",
    "renv",
    "tidyverse"
  ),
  here("packages.bib")
)
cat(c(readLines(here::here("packages.bib")), "\n", readLines(here::here("references.bib"))), sep = "\n", file = "temp.bib")
```
